Modelling last glacial cycle ice dynamics in the Alps

### 2017-01-25 articles/cycle/alps-cycle.tex
Develop main text (one sentence per paragraph).

\section{Main}
\subsection{Introduction}
\subsection{Glacier dynamics}
    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.\\
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.\\
    Fig.~\ref{fig:profiles} -- Individual glacier extent profiles.
\subsection{Erosion potential}
    Fig.~\ref{fig:erosion} -- Integrated erosion potential.

\section{Methods}
\subsection{Ice sheet model set-up}
    Table~\ref{tab:params} -- Model parameters\\
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\
\subsection{Palaeo-climate forcing}
    Table~\ref{tab:records} -- Palaeo-climate records.\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.

>>>>

% ----------------------------------------------------------------------
\section{Main}
% ----------------------------------------------------------------------

\subsection{Introduction}

    \begin{itemize}
    \item The European Alps are the cradle of pioneer glacial studies.
    \item Today, their glacial history is better understood than any other.
    \item The LGM extent is very well known (Fig.~\ref{fig:lgmvel}a).
    \item But modelling was difficult due to the steep topography.
    \item Here, we us PISM to model the last glacial cycle (120--0\,ka).
    \end{itemize}

\subsection{Glacier dynamics}
    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.\\
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.\\
    Fig.~\ref{fig:profiles} -- Individual glacier extent profiles.

    \begin{itemize}
    \item Rapid variations of total ice volume (Fig.~\ref{fig:lgmvel}b).
    \item Two major glaciations during MIS 4 and 2 (Fig.~\ref{fig:lgmvel}b).
    \item Maximum stages flow pattern is complex (Fig.~\ref{fig:lgmvel}a).
    \item Maximum extent is farily well reproduced (Fig.~\ref{fig:lgmvel}a).
    \item Maximum extent is time-transgressive (Fig.~\ref{fig:timing}).
    \item Glaciers have different response times (Fig.~\ref{fig:timing}).
    \item Some glaciers advance many times (Fig.~\ref{fig:profiles}).
    \end{itemize}

\subsection{Erosion potential}
    Fig.~\ref{fig:erosion} -- Integrated erosion potential.

    \begin{itemize}
    \item We calculate erosion after \citet{Herman.etal.2015}
    \item More erosion in valleys of western Alps (Fig.~\ref{fig:erosion}a).
    \item Erosion is constant during 110--15\,ka (Fig.~\ref{fig:erosion}b).
    \end{itemize}

% ----------------------------------------------------------------------
\section{Methods}
% ----------------------------------------------------------------------

\subsection{Ice sheet model set-up}
    Table~\ref{tab:params} -- Model parameters\\
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\
\subsection{Palaeo-climate forcing}
    Table~\ref{tab:records} -- Palaeo-climate records.\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.
